plyranges: a grammar for transforming genomics data

### 2018-04-23 paper.Rmd
get rid of line

```{r titv-viz, echo = FALSE, fig.cap = "Dot plot of chromosomes ordered by estimated transition-transversion ratio. A white reference line is drawn at the expected ratio for a human exome."}
ti_tv_results %>% 
  as.data.frame() %>% 
  ggplot(aes(forcats::fct_reorder(seqnames, ti_tv), ti_tv)) +
  geom_point() + 
  geom_hline(yintercept = 3, colour = "white", size = 4) +
  labs(x = "Chromosome", y = "Transition Transverion Ratio") +
  coord_flip()

>>>>

```{r titv-viz, echo = FALSE, fig.cap = "Dot plot of chromosomes ordered by estimated transition-transversion ratio. A white reference line is drawn at the expected ratio for a human exome."}
ti_tv_results %>% 
  as.data.frame() %>% 
  ggplot(aes(forcats::fct_reorder(seqnames, ti_tv), ti_tv)) +
  geom_point() + 
  geom_hline(yintercept = 3, colour = "white", size = 4) +
  labs(x = "Chromosome", y = "Transition Transverion Ratio") +
  coord_flip() 
```
